\textbf{Access Control for Content Distribution Network Assets}

### 2016-05-25 tex/paper.tex
Small reviewer requested changes

\vspace{1em}
\textbf{File Read}
\vspace{1em}
\begin{equation} \label{eq:fileread}
    \inferrule
    {A[u,c] \\ C[c \cup \{m\}]} 
    {(C[c], F) \xrightarrow{u, read(f)} (C[c], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Update}
\vspace{1em}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {A[u,c] \\ m' = \{id = m.id, file = f'\} \\ \neg readOnly(c)} 
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, f')} ((C[c \cup \{m'\}], F \cup \{f'\}))}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Update}
\vspace{1em}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {A[u,c] \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, m')} ((C[c \cup \{m'\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Snapshot}
\vspace{1em}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        &snapshot(c) = \{c'.id = \textit{"fresh"}, snapshot(c') \mid c' \in c \} \cup \{ snapshot(m) \mid m \in c \}\\
        &snapshot({id = i, file = f }) = \{ id = \text{"fresh"}, file = f \} 
    \end{split}
\end{equation}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {A[u,c] \\ \neg readOnly(c)}
    {(C[c], F) \xrightarrow{u, copy(c)} (C[c \cup snapshot(c)], F)}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

>>>>

\vspace{1em}
\textbf{File Read}
\vspace{1em}
\begin{equation} \label{eq:fileread}
    \inferrule
    {A[u,c]]} 
    {(C[c \cup \{m\}], F) \xrightarrow{u, read(f)} (C[c \cup \{m\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Update}
\vspace{1em}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {A[u,c] \\ m' = \{id = m.id, file = f'\} \\ \neg readOnly(c)} 
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, f')} (C[c \cup \{m'\}], F \cup \{f'\})}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Update}
\vspace{1em}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {A[u,c] \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, m')} (C[c \cup \{m'\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Snapshot}
\vspace{1em}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        &snapshot(c) = \{snapshot(c') \mid c' \in c \} \cup \{ snapshot(m) \mid m \in c \}\\
        &snapshot({id = i, file = f }) = \{ id = \text{"fresh"}, file = f \} 
    \end{split}
\end{equation}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {A[u,c] \\ \neg readOnly(c)}
    {(C[c], F) \xrightarrow{u, copy(c)} (C[c, snapshot(c)], F)}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.
